### 2015-05-26 writing/SNLI paper/corpus.tex

% I suggest removing this sentence. It sounds like a negative, but
% there is no practical alternative except what we did do.
%
% The majority of the sentence pairs in the corpus have not been reviewed by anyone since their construction as part of the data collection Mechanical Turk task, except to remove a small number of cases where either a response field was empty or the original author flagged the source caption for review.
In order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we performed an additional round of validation for about 10\% of our data.
This validation phase was not fundamentally different from the Mechanical Turk labeling task used to label the SICK entailment data: we presented workers with pairs of sentences (in our case, in batches of five at a time), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original author. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ. Though we used a very restrictive qualification (based on past approval rate) to select workers, we nonetheless discovered and deleted some instances of random guessing during an early round of validation, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.
\todo{Leave in mention of qual? I would--CP}

For each pair that we validated, we chose a gold label. If any one of the three labels was chosen by at least three of the five annotators, that label is the gold label. If there was no such consensus, which occurred in about 0.2\% of cases, we chose the label `-'. While these unlabeled examples are included in the corpus distribution, they are unlikely to be helpful for the standard NLI classification task, and we do not include them when training and evaluating the models discussed in later sections. The results of this validation process are summarized in Tables \ref{validation-stats}, and \ref{validation-freq}, and suggest that while fundamental limits of both our crowdsourcing methods and the task itself impose an upper bound on the consistency of our labels, the data is sufficiently high quality to pose a challenging but realistic machine learning task.

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l lll} 
    \toprule
\textbf{Label} & \textbf{Train} & \textbf{Dev} & \textbf{Test}\\
\midrule
\ii{entailment} &		33.3 & 	33.3 & 	33.7 \\
\ii{neutral} & 		33.2 & 	32.4 & 	32.2 \\
\ii{contradiction} &  	33.3 & 	32.7 & 	32.4  \\
- (no consensus) & 	0.1 & 	1.6 & 	1.8 \\
\bottomrule
  \end{tabular}	
% From 1.0rc3
\caption{\label{validation-freq}Frequency (\%) of each label in the corpus. Note that examples without gold labels are omitted in standard evaluations.} 
\end{table}

>>>>

% I suggest removing this sentence. It sounds like a negative, but
% there is no practical alternative except what we did do.
%
% The majority of the sentence pairs in the corpus have not been reviewed by anyone since their construction as part of the data collection Mechanical Turk task, except to remove a small number of cases where either a response field was empty or the original author flagged the source caption for review.
In order to measure the quality of our corpus, and in order to construct maximally useful testing and development sets, we performed an additional round of validation for about 10\% of our data.
This validation phase was not fundamentally different from the Mechanical Turk labeling task used to label the SICK entailment data: we presented workers with pairs of sentences (in our case, in batches of five), and ask them to choose a single label for each pair. We supplied each pair to four annonators, yielding five labels per pair including the label used by the original author. The instructions were broadly similar to the instructions for initial data collection shown in Fig.~\ref{instructions-1}, and linked to a similar FAQ. Though we used a very restrictive qualification (based on past approval rate) to select workers, we nonetheless discovered and deleted some instances of random guessing during an early round of validation, and subsequently instituted a fully closed qualification restricted to about 30 trusted workers.
\todo{Leave in mention of qual? I would--CP}

For each pair that we validated, we chose a gold label. If any one of
the three labels was chosen by at least three of the five annotators,
that label is the gold label. If there was no such consensus, which
occurred in about 0.2\% of cases, we chose the label `-'. While these
unlabeled examples are included in the corpus distribution, they are
unlikely to be helpful for the standard NLI classification task, and
we do not include them when training and evaluating the models
discussed in later sections. The results of this validation process
are summarized in Tables \ref{validation-stats} and
\ref{validation-freq}. Nearly all of the examples received a majority
label, indicating broad consensus about the nature of the data and
categories. The gold-labeled examples are essentially evenly
distributed across the three categories in our train, development, and
testing (Table~\ref{validation-freq}). The Fleiss $\kappa$ scores in
Table~\ref{kappas} are likely to be conservative given our large and
unevenly distributed pool of workers, but they still provide insights
about the levels of disagreement across the three semantic
classes. This disagreement likely reflects not just the limitations of
large crowdsourcing efforts but also the uncertainty inherent in NLI.
Regardless, the overall rates of agreement is extremely high,
suggesting that the corpus is sufficiently high quality to pose a
challenging but realistic machine learning task.

@@

%%%%% This is the first table I would cut to save space.
%%%%% I summarized its content quickly in the prose. CP
%
\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l lll} 
    \toprule
\textbf{Label} & \textbf{Train} & \textbf{Dev} & \textbf{Test}\\
\midrule
\ii{entailment} &		33.3 & 	33.3 & 	33.7 \\
\ii{neutral} & 		33.2 & 	32.4 & 	32.2 \\
\ii{contradiction} &  	33.3 & 	32.7 & 	32.4  \\
- (no consensus) & 	0.1 & 	1.6 & 	1.8 \\
\bottomrule
  \end{tabular}	
% From 1.0rc3
\caption{\label{validation-freq}Frequency (\%) of each label in the corpus. Note that examples without gold labels are omitted in standard evaluations.} 
\end{table}
